Opportunities for improvement in the care of adult trauma patients arriving in shock

### 2024-12-16 thesis.Rmd
La till master combined

```{r ISS confounding, echo=FALSE}
sample.characteristics.table_ISS
```

>>>>

```{r ISS confounding, echo=FALSE}
sample.characteristics.table_ISS_BE
sample.characteristics.table_ISS_SBP
```

DIVIDER

```{r masterBE, echo=FALSE}
master_combined_table_stepBE
```

DIVIDER

```{r masterSBP, echo=FALSE}
master_combined_table_stepSBP
```
